---
title: "Homework 1"
author:
  - "FirstName LastName Member 1"
  - "FirstName LastName Member 2"
  - "FirstName LastName Member 3"
  - "FirstName LastName Member 4"
date: "`r Sys.Date()`"
documentclass: article
geometry: margin=1in
fontsize: 11pt
output:
  pdf_document:
    toc: false
    df_print: kable
    fig_caption: false
    number_sections: false
    dev: pdf
    highlight: tango
  html_document:
    theme: default
    self_contained: true
    toc: false
    df_print: kable
    fig_caption: false
    number_sections: false
    smart: true
    dev: svg
---

```{r setup, include = FALSE}
# DO NOT ALTER THIS CHUNK
knitr::opts_chunk$set(
  echo = TRUE,
  eval = TRUE,
  fig.width = 5,
  fig.asp = 0.618,
  out.width = "70%",
  dpi = 120,
  fig.align = "center",
  cache = FALSE
)
# Load required packages
suppressPackageStartupMessages(library(tidyverse))
# Load dataset
rail_trail <- read_rds("rail_trail.rds")
```

## Question 1




## Question 2




## Question 3




## Question 4




## Question 5




## Question 6




## Question 7




## Question 8




## Question 9




## Question 10
```{r}
ggplot(data = rail_trail) +
geom_point(
mapping = aes(
x = volume, 
y = hightemp
))
```

I see a right skewed, positive relationship between volume and temperature in this data set.

## Question 11

```{r}
ggplot(data = rail_trail) +
geom_point(
mapping = aes(
x = volume, 
y = hightemp,
color = weekday
))
```

```{r}
ggplot(data = rail_trail) +
geom_point(
mapping = aes(
x = volume, 
y = hightemp,
)) +
facet_grid(weekday ~ .)
```

Mapping by color would be preferable for smaller data sets where there is no overlap in data point values. Color mapping is also very easy on the eyes and would be good if you are doing a presentation to a group of people. Faceting would be more useful in a large data set where data points will be plotted over top of and may even be indiscernible from each other. Faceting would be useful for a scientist who wnats to account for every variable.

## Question 12

```{r}
ggplot(data = rail_trail) +
geom_smooth(
mapping = aes(
x = volume, 
y = hightemp,
)) +
facet_grid(weekday ~ .)
```


## Question 13




